---
layout:   post
title:    "散户之家"
category:  strategy
tags:     
    -  
    -   
description: 
published: false
status:    process
---


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(beepr)
library(rvest)
```

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- as.character( rep(NA,10) )        ## No. = 10，可以修改
for ( i in 1:length(url) ){
  url[i] <- paste("http://www.zf826.com/page/", i, sep="")
}

#############################################################
link <- function(x){
  x %>% 
  read_html() %>% 
  html_nodes(".fl") %>% 
  html_attr("href")
}
all <- lapply(url, link)
```
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[6]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[7]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[8]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[9]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`



<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`


<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[10]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-info span") %>% 
  html_text()
date <- date[1]

main <- url %>%
  read_html() %>%
  html_nodes("#single-con p") %>% 
  html_text()
###############################################################
main = gsub("———", "\n --------------------------------------------------------------------------------------------- \n", main)
main = gsub("-", "", main)
## main = paste(main, collapse = '\n ===================================================================================== \n')  
main = paste(main, collapse = '\n                                                                                              \n')
```

### `r title`
[`r date`](`r url`)

`r main`

<!------------------------------------------------------------------------------------------------------->


```{r echo=FALSE, warning=FALSE, message=FALSE}
beep()
```
