---
layout:   post
title:    "公司研究"
category: strategy
tags:     
    -  
    -   
description: 
published: false
status:    process
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
# if you do not have it already, install the devtools package install.packages("devtools") 
# devtools::install_github("hadley/rvest") 
library(rvest)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
url1 <- "http://stock.stockstar.com/list/3491_1.shtml"
url2 <- "http://stock.stockstar.com/list/3491_2.shtml"

link1 <- url1 %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listtable  li  a") %>% 
  html_attr("href")

link2 <- url2 %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listtable  li  a") %>% 
  html_attr("href")

link <- c(link1, link2)

article <- function(x){
  link <- x
  
  title  <- x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("h1") %>% 
    html_text()

  date <- x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("#pubtime_baidu") %>% 
    html_text()

  main <- x %>%
    read_html(encoding="GB18030")  %>% 
    html_nodes("#container-article  p") %>% 
    html_text() %>% 
    gsub("个股资料|操作策略|咨询高手|实盘买卖|相关附件", "", .) %>%
    gsub("(\\（|\\）)"," ..........................................................", .) %>% 
    paste(., collapse = '\n                                                                                              \n')

  file <-  x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("#container-article  p  a") %>% 
    html_attr("href") %>%
    .[1]

  file.link <-  x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("#container-article  p  a") %>% 
    html_text() %>%
    .[1]

  all <- list(link, title, date, main, file, file.link)   ## all information: link, title, date, main
  return(all)
}

inf = lapply(link, article)
##:
## inf[[]][[1]]: link
## inf[[]][[2]]: title
## inf[[]][[3]]: date
## inf[[]][[4]]: main
## inf[[]][[5]]: file
## inf[[]][[6]]: file.link
```

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[1]][[2]]` </h3>
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

[`r inf[[1]][[6]]`](`r inf[[1]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[2]][[2]]` </h3>
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

[`r inf[[2]][[6]]`](`r inf[[2]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[3]][[2]]` </h3>
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

[`r inf[[3]][[6]]`](`r inf[[3]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[4]][[2]]` </h3>
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

[`r inf[[4]][[6]]`](`r inf[[4]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[5]][[2]]` </h3>
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

[`r inf[[5]][[6]]`](`r inf[[6]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[6]][[2]]` </h3>
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

[`r inf[[6]][[6]]`](`r inf[[6]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[7]][[2]]` </h3>
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

[`r inf[[7]][[6]]`](`r inf[[7]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[8]][[2]]` </h3>
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

[`r inf[[8]][[6]]`](`r inf[[8]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[9]][[2]]` </h3>
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

[`r inf[[9]][[6]]`](`r inf[[9]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[10]][[2]]` </h3>
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

[`r inf[[10]][[6]]`](`r inf[[10]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[11]][[2]]` </h3>
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

[`r inf[[11]][[6]]`](`r inf[[11]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[12]][[2]]` </h3>
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

[`r inf[[12]][[6]]`](`r inf[[12]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[13]][[2]]` </h3>
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

[`r inf[[13]][[6]]`](`r inf[[13]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[14]][[2]]` </h3>
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

[`r inf[[14]][[6]]`](`r inf[[14]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[15]][[2]]` </h3>
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

[`r inf[[15]][[6]]`](`r inf[[15]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[16]][[2]]` </h3>
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

[`r inf[[16]][[6]]`](`r inf[[16]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[17]][[2]]` </h3>
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

[`r inf[[17]][[6]]`](`r inf[[17]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[18]][[2]]` </h3>
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

[`r inf[[18]][[6]]`](`r inf[[18]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[19]][[2]]` </h3>
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

[`r inf[[19]][[6]]`](`r inf[[19]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[20]][[2]]` </h3>
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

[`r inf[[20]][[6]]`](`r inf[[20]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[21]][[2]]` </h3>
[`r inf[[21]][[3]]`](`r inf[[21]][[1]]`)

`r inf[[21]][[4]]`

[`r inf[[21]][[6]]`](`r inf[[21]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[22]][[2]]` </h3>
[`r inf[[22]][[3]]`](`r inf[[22]][[1]]`)

`r inf[[22]][[4]]`

[`r inf[[22]][[6]]`](`r inf[[22]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[23]][[2]]` </h3>
[`r inf[[23]][[3]]`](`r inf[[23]][[1]]`)

`r inf[[23]][[4]]`

[`r inf[[23]][[6]]`](`r inf[[23]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[24]][[2]]` </h3>
[`r inf[[24]][[3]]`](`r inf[[24]][[1]]`)

`r inf[[24]][[4]]`

[`r inf[[24]][[6]]`](`r inf[[24]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[25]][[2]]` </h3>
[`r inf[[25]][[3]]`](`r inf[[25]][[1]]`)

`r inf[[25]][[4]]`

[`r inf[[25]][[6]]`](`r inf[[25]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[26]][[2]]` </h3>
[`r inf[[26]][[3]]`](`r inf[[26]][[1]]`)

`r inf[[26]][[4]]`

[`r inf[[26]][[6]]`](`r inf[[26]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[27]][[2]]` </h3>
[`r inf[[27]][[3]]`](`r inf[[27]][[1]]`)

`r inf[[27]][[4]]`

[`r inf[[27]][[6]]`](`r inf[[27]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[28]][[2]]` </h3>
[`r inf[[28]][[3]]`](`r inf[[28]][[1]]`)

`r inf[[28]][[4]]`

[`r inf[[28]][[6]]`](`r inf[[28]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[29]][[2]]` </h3>
[`r inf[[29]][[3]]`](`r inf[[29]][[1]]`)

`r inf[[29]][[4]]`

[`r inf[[29]][[6]]`](`r inf[[29]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[30]][[2]]` </h3>
[`r inf[[30]][[3]]`](`r inf[[30]][[1]]`)

`r inf[[30]][[4]]`

[`r inf[[30]][[6]]`](`r inf[[30]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[31]][[2]]` </h3>
[`r inf[[31]][[3]]`](`r inf[[31]][[1]]`)

`r inf[[31]][[4]]`

[`r inf[[31]][[6]]`](`r inf[[31]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[32]][[2]]` </h3>
[`r inf[[32]][[3]]`](`r inf[[32]][[1]]`)

`r inf[[32]][[4]]`

[`r inf[[32]][[6]]`](`r inf[[32]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[33]][[2]]` </h3>
[`r inf[[33]][[3]]`](`r inf[[33]][[1]]`)

`r inf[[33]][[4]]`

[`r inf[[33]][[6]]`](`r inf[[33]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[34]][[2]]` </h3>
[`r inf[[34]][[3]]`](`r inf[[34]][[1]]`)

`r inf[[34]][[4]]`

[`r inf[[34]][[6]]`](`r inf[[34]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[35]][[2]]` </h3>
[`r inf[[35]][[3]]`](`r inf[[35]][[1]]`)

`r inf[[35]][[4]]`

[`r inf[[35]][[6]]`](`r inf[[35]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[36]][[2]]` </h3>
[`r inf[[36]][[3]]`](`r inf[[36]][[1]]`)

`r inf[[36]][[4]]`

[`r inf[[36]][[6]]`](`r inf[[36]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[37]][[2]]` </h3>
[`r inf[[37]][[3]]`](`r inf[[37]][[1]]`)

`r inf[[37]][[4]]`

[`r inf[[37]][[6]]`](`r inf[[37]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[38]][[2]]` </h3>
[`r inf[[38]][[3]]`](`r inf[[38]][[1]]`)

`r inf[[38]][[4]]`

[`r inf[[38]][[6]]`](`r inf[[38]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[39]][[2]]` </h3>
[`r inf[[39]][[3]]`](`r inf[[39]][[1]]`)

`r inf[[39]][[4]]`

[`r inf[[39]][[6]]`](`r inf[[39]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[40]][[2]]` </h3>
[`r inf[[40]][[3]]`](`r inf[[40]][[1]]`)

`r inf[[40]][[4]]`

[`r inf[[40]][[6]]`](`r inf[[40]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[41]][[2]]` </h3>
[`r inf[[41]][[3]]`](`r inf[[41]][[1]]`)

`r inf[[41]][[4]]`

[`r inf[[41]][[6]]`](`r inf[[41]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[42]][[2]]` </h3>
[`r inf[[42]][[3]]`](`r inf[[42]][[1]]`)

`r inf[[42]][[4]]`

[`r inf[[42]][[6]]`](`r inf[[42]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[43]][[2]]` </h3>
[`r inf[[43]][[3]]`](`r inf[[43]][[1]]`)

`r inf[[43]][[4]]`

[`r inf[[43]][[6]]`](`r inf[[43]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[44]][[2]]` </h3>
[`r inf[[44]][[3]]`](`r inf[[44]][[1]]`)

`r inf[[44]][[4]]`

[`r inf[[44]][[6]]`](`r inf[[44]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[45]][[2]]` </h3>
[`r inf[[45]][[3]]`](`r inf[[45]][[1]]`)

`r inf[[45]][[4]]`

[`r inf[[45]][[6]]`](`r inf[[45]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[46]][[2]]` </h3>
[`r inf[[46]][[3]]`](`r inf[[46]][[1]]`)

`r inf[[46]][[4]]`

[`r inf[[46]][[6]]`](`r inf[[46]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[47]][[2]]` </h3>
[`r inf[[47]][[3]]`](`r inf[[47]][[1]]`)

`r inf[[47]][[4]]`

[`r inf[[47]][[6]]`](`r inf[[47]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[48]][[2]]` </h3>
[`r inf[[48]][[3]]`](`r inf[[48]][[1]]`)

`r inf[[48]][[4]]`

[`r inf[[48]][[6]]`](`r inf[[48]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[49]][[2]]` </h3>
[`r inf[[49]][[3]]`](`r inf[[49]][[1]]`)

`r inf[[49]][[4]]`

[`r inf[[49]][[6]]`](`r inf[[49]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[50]][[2]]` </h3>
[`r inf[[50]][[3]]`](`r inf[[50]][[1]]`)

`r inf[[50]][[4]]`

[`r inf[[50]][[6]]`](`r inf[[50]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[51]][[2]]` </h3>
[`r inf[[51]][[3]]`](`r inf[[51]][[1]]`)

`r inf[[51]][[4]]`

[`r inf[[51]][[6]]`](`r inf[[51]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[52]][[2]]` </h3>
[`r inf[[52]][[3]]`](`r inf[[52]][[1]]`)

`r inf[[52]][[4]]`

[`r inf[[52]][[6]]`](`r inf[[52]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[53]][[2]]` </h3>
[`r inf[[53]][[3]]`](`r inf[[53]][[1]]`)

`r inf[[53]][[4]]`

[`r inf[[53]][[6]]`](`r inf[[53]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[54]][[2]]` </h3>
[`r inf[[54]][[3]]`](`r inf[[54]][[1]]`)

`r inf[[54]][[4]]`

[`r inf[[54]][[6]]`](`r inf[[54]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[55]][[2]]` </h3>
[`r inf[[55]][[3]]`](`r inf[[55]][[1]]`)

`r inf[[55]][[4]]`

[`r inf[[55]][[6]]`](`r inf[[55]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[56]][[2]]` </h3>
[`r inf[[56]][[3]]`](`r inf[[56]][[1]]`)

`r inf[[56]][[4]]`

[`r inf[[56]][[6]]`](`r inf[[56]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[57]][[2]]` </h3>
[`r inf[[57]][[3]]`](`r inf[[57]][[1]]`)

`r inf[[57]][[4]]`

[`r inf[[57]][[6]]`](`r inf[[57]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[58]][[2]]` </h3>
[`r inf[[58]][[3]]`](`r inf[[58]][[1]]`)

`r inf[[58]][[4]]`

[`r inf[[58]][[6]]`](`r inf[[58]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[59]][[2]]` </h3>
[`r inf[[59]][[3]]`](`r inf[[59]][[1]]`)

`r inf[[59]][[4]]`

[`r inf[[59]][[6]]`](`r inf[[59]][[5]]`)
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[60]][[2]]` </h3>
[`r inf[[60]][[3]]`](`r inf[[60]][[1]]`)

`r inf[[60]][[4]]`

[`r inf[[60]][[6]]`](`r inf[[60]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[61]][[2]]` </h3>
[`r inf[[61]][[3]]`](`r inf[[61]][[1]]`)

`r inf[[61]][[4]]`

[`r inf[[61]][[6]]`](`r inf[[61]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[62]][[2]]` </h3>
[`r inf[[62]][[3]]`](`r inf[[62]][[1]]`)

`r inf[[62]][[4]]`

[`r inf[[62]][[6]]`](`r inf[[62]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[63]][[2]]` </h3>
[`r inf[[63]][[3]]`](`r inf[[63]][[1]]`)

`r inf[[63]][[4]]`

[`r inf[[63]][[6]]`](`r inf[[63]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[64]][[2]]` </h3>
[`r inf[[64]][[3]]`](`r inf[[64]][[1]]`)

`r inf[[64]][[4]]`

[`r inf[[64]][[6]]`](`r inf[[64]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[65]][[2]]` </h3>
[`r inf[[65]][[3]]`](`r inf[[65]][[1]]`)

`r inf[[65]][[4]]`

[`r inf[[65]][[6]]`](`r inf[[65]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[66]][[2]]` </h3>
[`r inf[[66]][[3]]`](`r inf[[66]][[1]]`)

`r inf[[66]][[4]]`

[`r inf[[66]][[6]]`](`r inf[[66]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[67]][[2]]` </h3>
[`r inf[[67]][[3]]`](`r inf[[67]][[1]]`)

`r inf[[67]][[4]]`

[`r inf[[67]][[6]]`](`r inf[[67]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[68]][[2]]` </h3>
[`r inf[[68]][[3]]`](`r inf[[68]][[1]]`)

`r inf[[68]][[4]]`

[`r inf[[68]][[6]]`](`r inf[[68]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[69]][[2]]` </h3>
[`r inf[[69]][[3]]`](`r inf[[69]][[1]]`)

`r inf[[69]][[4]]`

[`r inf[[69]][[6]]`](`r inf[[69]][[5]]`)
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[70]][[2]]` </h3>
[`r inf[[70]][[3]]`](`r inf[[70]][[1]]`)

`r inf[[70]][[4]]`

[`r inf[[70]][[6]]`](`r inf[[70]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[71]][[2]]` </h3>
[`r inf[[71]][[3]]`](`r inf[[71]][[1]]`)

`r inf[[71]][[4]]`

[`r inf[[71]][[6]]`](`r inf[[71]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[72]][[2]]` </h3>
[`r inf[[72]][[3]]`](`r inf[[72]][[1]]`)

`r inf[[72]][[4]]`

[`r inf[[72]][[6]]`](`r inf[[72]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[73]][[2]]` </h3>
[`r inf[[73]][[3]]`](`r inf[[73]][[1]]`)

`r inf[[73]][[4]]`

[`r inf[[73]][[6]]`](`r inf[[73]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[74]][[2]]` </h3>
[`r inf[[74]][[3]]`](`r inf[[74]][[1]]`)

`r inf[[74]][[4]]`

[`r inf[[74]][[6]]`](`r inf[[74]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[75]][[2]]` </h3>
[`r inf[[75]][[3]]`](`r inf[[75]][[1]]`)

`r inf[[75]][[4]]`

[`r inf[[75]][[6]]`](`r inf[[75]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[76]][[2]]` </h3>
[`r inf[[76]][[3]]`](`r inf[[76]][[1]]`)

`r inf[[76]][[4]]`

[`r inf[[76]][[6]]`](`r inf[[76]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[77]][[2]]` </h3>
[`r inf[[77]][[3]]`](`r inf[[77]][[1]]`)

`r inf[[77]][[4]]`

[`r inf[[77]][[6]]`](`r inf[[77]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[78]][[2]]` </h3>
[`r inf[[78]][[3]]`](`r inf[[78]][[1]]`)

`r inf[[78]][[4]]`

[`r inf[[78]][[6]]`](`r inf[[78]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[79]][[2]]` </h3>
[`r inf[[79]][[3]]`](`r inf[[79]][[1]]`)

`r inf[[79]][[4]]`

[`r inf[[79]][[6]]`](`r inf[[79]][[5]]`)
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[80]][[2]]` </h3>
[`r inf[[80]][[3]]`](`r inf[[80]][[1]]`)

`r inf[[80]][[4]]`

[`r inf[[80]][[6]]`](`r inf[[80]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[81]][[2]]` </h3>
[`r inf[[81]][[3]]`](`r inf[[81]][[1]]`)

`r inf[[81]][[4]]`

[`r inf[[81]][[6]]`](`r inf[[81]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[82]][[2]]` </h3>
[`r inf[[82]][[3]]`](`r inf[[82]][[1]]`)

`r inf[[82]][[4]]`

[`r inf[[82]][[6]]`](`r inf[[82]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[83]][[2]]` </h3>
[`r inf[[83]][[3]]`](`r inf[[83]][[1]]`)

`r inf[[83]][[4]]`

[`r inf[[83]][[6]]`](`r inf[[83]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[84]][[2]]` </h3>
[`r inf[[84]][[3]]`](`r inf[[84]][[1]]`)

`r inf[[84]][[4]]`

[`r inf[[84]][[6]]`](`r inf[[84]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[85]][[2]]` </h3>
[`r inf[[85]][[3]]`](`r inf[[85]][[1]]`)

`r inf[[85]][[4]]`

[`r inf[[85]][[6]]`](`r inf[[85]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[86]][[2]]` </h3>
[`r inf[[86]][[3]]`](`r inf[[86]][[1]]`)

`r inf[[86]][[4]]`

[`r inf[[86]][[6]]`](`r inf[[86]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[87]][[2]]` </h3>
[`r inf[[87]][[3]]`](`r inf[[87]][[1]]`)

`r inf[[87]][[4]]`

[`r inf[[87]][[6]]`](`r inf[[87]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[88]][[2]]` </h3>
[`r inf[[88]][[3]]`](`r inf[[88]][[1]]`)

`r inf[[88]][[4]]`

[`r inf[[88]][[6]]`](`r inf[[88]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[89]][[2]]` </h3>
[`r inf[[89]][[3]]`](`r inf[[89]][[1]]`)

`r inf[[89]][[4]]`

[`r inf[[89]][[6]]`](`r inf[[89]][[5]]`)
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[90]][[2]]` </h3>
[`r inf[[90]][[3]]`](`r inf[[90]][[1]]`)

`r inf[[90]][[4]]`

[`r inf[[90]][[6]]`](`r inf[[90]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[91]][[2]]` </h3>
[`r inf[[91]][[3]]`](`r inf[[91]][[1]]`)

`r inf[[91]][[4]]`

[`r inf[[91]][[6]]`](`r inf[[91]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[92]][[2]]` </h3>
[`r inf[[92]][[3]]`](`r inf[[92]][[1]]`)

`r inf[[92]][[4]]`

[`r inf[[92]][[6]]`](`r inf[[92]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[93]][[2]]` </h3>
[`r inf[[93]][[3]]`](`r inf[[93]][[1]]`)

`r inf[[93]][[4]]`

[`r inf[[93]][[6]]`](`r inf[[93]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[94]][[2]]` </h3>
[`r inf[[94]][[3]]`](`r inf[[94]][[1]]`)

`r inf[[94]][[4]]`

[`r inf[[94]][[6]]`](`r inf[[94]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[95]][[2]]` </h3>
[`r inf[[95]][[3]]`](`r inf[[95]][[1]]`)

`r inf[[95]][[4]]`

[`r inf[[95]][[6]]`](`r inf[[95]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[96]][[2]]` </h3>
[`r inf[[96]][[3]]`](`r inf[[96]][[1]]`)

`r inf[[96]][[4]]`

[`r inf[[96]][[6]]`](`r inf[[96]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[97]][[2]]` </h3>
[`r inf[[97]][[3]]`](`r inf[[97]][[1]]`)

`r inf[[97]][[4]]`

[`r inf[[97]][[6]]`](`r inf[[97]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[98]][[2]]` </h3>
[`r inf[[98]][[3]]`](`r inf[[98]][[1]]`)

`r inf[[98]][[4]]`

[`r inf[[98]][[6]]`](`r inf[[98]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[99]][[2]]` </h3>
[`r inf[[99]][[3]]`](`r inf[[99]][[1]]`)

`r inf[[99]][[4]]`

[`r inf[[99]][[6]]`](`r inf[[99]][[5]]`)
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

<h3> `r inf[[100]][[2]]` </h3>
[`r inf[[100]][[3]]`](`r inf[[100]][[1]]`)

`r inf[[100]][[4]]`

[`r inf[[100]][[6]]`](`r inf[[100]][[5]]`)

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->


```{r echo=FALSE, warning=FALSE, message=FALSE}
# install.packages("beepr")
library(beepr)
beep()
```
