---
layout:   post
title:    "财经头条"
category:  
tags:     
    -  
    -   
description: 
published: false
status:    process
---

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<base target=”_blank”/>

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(rvest)
library(beepr)
```
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

# 证券之星

## 证券要闻====================================
```{r echo=FALSE, warning=FALSE, message=FALSE}
article <- function(x){
  link <- x
  
  title  <- x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("h1") %>% 
    html_text()
  
  date <- x %>% 
    read_html(encoding="GB18030") %>% 
    html_nodes("#pubtime_baidu") %>% 
    html_text()

  main <- x %>%
    read_html(encoding="GB18030")  %>% 
    html_nodes("#container-article  p") %>% 
    html_text() %>% 
    gsub("个股资料|操作策略|咨询高手|实盘买卖", "", .) %>% 
    gsub("(\\（|\\）)"," ..........................................................", .)  %>% 
    paste(., collapse = '\n                                                                                 \n')
  
  all <- list(link, title, date, main)   ## all information: link, title, date, main
  return(all)
}

## inf = lapply(link, article)
##:
## inf[[]][[1]]: link
## inf[[]][[2]]: title
## inf[[]][[3]]: date
## inf[[]][[4]]: main
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://stock.stockstar.com/list/2.shtml"       ## 证券要闻

link <- url %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listnews li a") %>% 
  html_attr("href") %>% 
  .[1:20]

inf = lapply(link, article)
```

<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[11]][[2]]`
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[12]][[2]]`
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[13]][[2]]`
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[14]][[2]]`
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[15]][[2]]`
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[16]][[2]]`
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[17]][[2]]`
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[18]][[2]]`
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[19]][[2]]`
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[20]][[2]]`
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

<!------------------------------------------------------------------------------------------------------->


## 趋势策略====================================

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://stock.stockstar.com/list/strategy.htm"       ## 趋势策略

link <- url %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listnews li a") %>% 
  html_attr("href") %>% 
  .[1:10]

inf = lapply(link, article)
```

<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->


## 公司新闻====================================

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://stock.stockstar.com/list/10.shtml"       ## 公司新闻

link <- url %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listnews li a") %>% 
  html_attr("href") %>% 
  .[1:20]

inf = lapply(link, article)
```

<!------------------------------------------------------------------------------------------------------->


### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[11]][[2]]`
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[12]][[2]]`
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[13]][[2]]`
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[14]][[2]]`
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[15]][[2]]`
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[16]][[2]]`
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[17]][[2]]`
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[18]][[2]]`
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[19]][[2]]`
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[20]][[2]]`
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->
## 散户之家·早晚报=============================

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://www.zf826.com/category/zf1"
link <- url %>% 
  read_html() %>% 
  html_nodes(".post-list-title   .fl") %>% 
  html_attr("href")

article <- function(x){
  link <- x
  
  title  <- x %>% 
    read_html() %>% 
    html_nodes(".single-title") %>% 
    html_text()

  date <- x %>% 
    read_html() %>% 
    html_nodes(".single-info   span") %>% 
    html_text() %>%
    .[1]

  main <- x %>%
    read_html()  %>% 
    html_nodes("#single-con   p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n')

  all <- list(link, title, date, main)   ## all information: link, title, date, main
  return(all)
}

inf <- lapply(link[1:5], article)
```

<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
# 东方财富
## 要闻精华====================================

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://finance.eastmoney.com/yaowen_cywjh.html"             ## 要闻精华

#############################################################
link <- url %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".title a") %>% 
  html_attr("href")

article <- function(x){
  link <- x
  
  title <- x %>%
    read_html(encoding="GB18030") %>%
    html_nodes(".newsContent  h1") %>% 
    html_text()

  date <- x %>%
    read_html(encoding="GB18030") %>%
    html_nodes(".Info span") %>% 
    html_text()
  date <- date[1]

  main <- x %>%
    read_html(encoding="GB18030") %>%
    html_nodes(".newsContent  p") %>% 
    html_text()
  main = paste(main, collapse = '\n                                                                                              \n')
  
  all <- list(link, title, date, main)   ## all information: link, title, date, main
  return(all)
}

inf = lapply(link, article)
##:
## inf[[]][[1]]: link
## inf[[]][[2]]: title
## inf[[]][[3]]: date
## inf[[]][[4]]: main
```
<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[11]][[2]]`
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[12]][[2]]`
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[13]][[2]]`
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[14]][[2]]`
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[15]][[2]]`
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[16]][[2]]`
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[17]][[2]]`
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[18]][[2]]`
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[19]][[2]]`
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[20]][[2]]`
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

<!------------------------------------------------------------------------------------------------------->


## 上市公司====================================
```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://finance.eastmoney.com/news/cssgs.html"

#############################################################
link <- url %>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".listBox  li  a") %>% 
  html_attr("href")

inf = lapply(link, article)
##:
## inf[[]][[1]]: link
## inf[[]][[2]]: title
## inf[[]][[3]]: date
## inf[[]][[4]]: main
```
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[11]][[2]]`
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[12]][[2]]`
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[13]][[2]]`
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[14]][[2]]`
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[15]][[2]]`
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[16]][[2]]`
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[17]][[2]]`
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[18]][[2]]`
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[19]][[2]]`
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[20]][[2]]`
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[21]][[2]]`
[`r inf[[21]][[3]]`](`r inf[[21]][[1]]`)

`r inf[[21]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[22]][[2]]`
[`r inf[[22]][[3]]`](`r inf[[22]][[1]]`)

`r inf[[22]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[23]][[2]]`
[`r inf[[23]][[3]]`](`r inf[[23]][[1]]`)

`r inf[[23]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[24]][[2]]`
[`r inf[[24]][[3]]`](`r inf[[24]][[1]]`)

`r inf[[24]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[25]][[2]]`
[`r inf[[25]][[3]]`](`r inf[[25]][[1]]`)

`r inf[[25]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[26]][[2]]`
[`r inf[[26]][[3]]`](`r inf[[26]][[1]]`)

`r inf[[26]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[27]][[2]]`
[`r inf[[27]][[3]]`](`r inf[[27]][[1]]`)

`r inf[[27]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[28]][[2]]`
[`r inf[[28]][[3]]`](`r inf[[28]][[1]]`)

`r inf[[28]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[29]][[2]]`
[`r inf[[29]][[3]]`](`r inf[[29]][[1]]`)

`r inf[[29]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[30]][[2]]`
[`r inf[[30]][[3]]`](`r inf[[30]][[1]]`)

`r inf[[30]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[31]][[2]]`
[`r inf[[31]][[3]]`](`r inf[[31]][[1]]`)

`r inf[[31]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[32]][[2]]`
[`r inf[[32]][[3]]`](`r inf[[32]][[1]]`)

`r inf[[32]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[33]][[2]]`
[`r inf[[33]][[3]]`](`r inf[[33]][[1]]`)

`r inf[[33]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[34]][[2]]`
[`r inf[[34]][[3]]`](`r inf[[34]][[1]]`)

`r inf[[34]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[35]][[2]]`
[`r inf[[35]][[3]]`](`r inf[[35]][[1]]`)

`r inf[[35]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[36]][[2]]`
[`r inf[[36]][[3]]`](`r inf[[36]][[1]]`)

`r inf[[36]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[37]][[2]]`
[`r inf[[37]][[3]]`](`r inf[[37]][[1]]`)

`r inf[[37]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[38]][[2]]`
[`r inf[[38]][[3]]`](`r inf[[38]][[1]]`)

`r inf[[38]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[39]][[2]]`
[`r inf[[39]][[3]]`](`r inf[[39]][[1]]`)

`r inf[[39]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[40]][[2]]`
[`r inf[[40]][[3]]`](`r inf[[40]][[1]]`)

`r inf[[40]][[4]]`

<!------------------------------------------------------------------------------------------------------->


### `r inf[[41]][[2]]`
[`r inf[[41]][[3]]`](`r inf[[41]][[1]]`)

`r inf[[41]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[42]][[2]]`
[`r inf[[42]][[3]]`](`r inf[[42]][[1]]`)

`r inf[[42]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[43]][[2]]`
[`r inf[[43]][[3]]`](`r inf[[43]][[1]]`)

`r inf[[43]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[44]][[2]]`
[`r inf[[44]][[3]]`](`r inf[[44]][[1]]`)

`r inf[[44]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[45]][[2]]`
[`r inf[[45]][[3]]`](`r inf[[45]][[1]]`)

`r inf[[45]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[46]][[2]]`
[`r inf[[46]][[3]]`](`r inf[[46]][[1]]`)

`r inf[[46]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[47]][[2]]`
[`r inf[[47]][[3]]`](`r inf[[47]][[1]]`)

`r inf[[47]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[48]][[2]]`
[`r inf[[48]][[3]]`](`r inf[[48]][[1]]`)

`r inf[[48]][[4]]`

<!------------------------------------------------------------------------------------------------------->
## 产业透视====================================
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- "http://finance.eastmoney.com/pinglun_ccyts.html"

#############################################################
link <- url%>% 
  read_html(encoding="GB18030") %>% 
  html_nodes(".title a") %>% 
  html_attr("href")

inf = lapply(link, article)
##:
## inf[[]][[1]]: link
## inf[[]][[2]]: title
## inf[[]][[3]]: date
## inf[[]][[4]]: main
```
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->

<!------------------------------------------------------------------------------------------------------->

### `r inf[[1]][[2]]`
[`r inf[[1]][[3]]`](`r inf[[1]][[1]]`)

`r inf[[1]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[2]][[2]]`
[`r inf[[2]][[3]]`](`r inf[[2]][[1]]`)

`r inf[[2]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[3]][[2]]`
[`r inf[[3]][[3]]`](`r inf[[3]][[1]]`)

`r inf[[3]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[4]][[2]]`
[`r inf[[4]][[3]]`](`r inf[[4]][[1]]`)

`r inf[[4]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[5]][[2]]`
[`r inf[[5]][[3]]`](`r inf[[5]][[1]]`)

`r inf[[5]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[6]][[2]]`
[`r inf[[6]][[3]]`](`r inf[[6]][[1]]`)

`r inf[[6]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[7]][[2]]`
[`r inf[[7]][[3]]`](`r inf[[7]][[1]]`)

`r inf[[7]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[8]][[2]]`
[`r inf[[8]][[3]]`](`r inf[[8]][[1]]`)

`r inf[[8]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[9]][[2]]`
[`r inf[[9]][[3]]`](`r inf[[9]][[1]]`)

`r inf[[9]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[10]][[2]]`
[`r inf[[10]][[3]]`](`r inf[[10]][[1]]`)

`r inf[[10]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[11]][[2]]`
[`r inf[[11]][[3]]`](`r inf[[11]][[1]]`)

`r inf[[11]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[12]][[2]]`
[`r inf[[12]][[3]]`](`r inf[[12]][[1]]`)

`r inf[[12]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[13]][[2]]`
[`r inf[[13]][[3]]`](`r inf[[13]][[1]]`)

`r inf[[13]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[14]][[2]]`
[`r inf[[14]][[3]]`](`r inf[[14]][[1]]`)

`r inf[[14]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[15]][[2]]`
[`r inf[[15]][[3]]`](`r inf[[15]][[1]]`)

`r inf[[15]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[16]][[2]]`
[`r inf[[16]][[3]]`](`r inf[[16]][[1]]`)

`r inf[[16]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[17]][[2]]`
[`r inf[[17]][[3]]`](`r inf[[17]][[1]]`)

`r inf[[17]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[18]][[2]]`
[`r inf[[18]][[3]]`](`r inf[[18]][[1]]`)

`r inf[[18]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[19]][[2]]`
[`r inf[[19]][[3]]`](`r inf[[19]][[1]]`)

`r inf[[19]][[4]]`

<!------------------------------------------------------------------------------------------------------->

### `r inf[[20]][[2]]`
[`r inf[[20]][[3]]`](`r inf[[20]][[1]]`)

`r inf[[20]][[4]]`

<!------------------------------------------------------------------------------------------------------->












<!------------------------------------------------------------------------------------------------------->
<!------------------------------------------------------------------------------------------------------->
```{r echo=FALSE, warning=FALSE, message=FALSE}
beep()
```
